\documentclass{my_cv}
\usepackage[skins]{tcolorbox}

\begin{document}
\begin{multicols}{2}[
    \titletext{Jonathan}%
        {Schweder}%
        {Data Scientist}%
        {cv@codeep.blue}%
        {+353 083 0748404}%
        {jaswdr}%
        {jaswdr.dev}%
]
\end{multicols}

\section{\faFileText}{SUMMARY}
Experienced Software Engineer with extensive IT experience. Skills include proficiency in many programming languages, virtualization, analytic thinking and creative problem-solving. Able to apply customer service concepts to IT to enhance user experience for customers, employees and administration.

\begin{multicols}{2}
\section{\faPencil}{WORK}

\work{System's Development Engineer / Mar 2020 - current}%
    {Dublin - Ireland}%
    {Developed workflow tools to deal with hundreds of thousands of network devices every day.}
    {Python, PostgreSQL, DynamoDB, CloudWatch, CloudFormation, Lambda, S3, EC2, ECS}

\work{Software Engineer / Feb 2019 - Mar 2020}%
    {Pantacor - London, UK}%
    {Worked on IoT management platform to enable customer to build, deploy and monitor remote fleets.}%
    {Go, Kubernetes, Docker, Kafka, Grafana Prometheus, MongoDB}

\work{Software Engineer / Jun 2018 - Feb 2019}%
    {Eventials - Blumenau, Santa Catarina, Brazil}%
    {Built multiple web application to government, contractors, driving schools and license plate manufacturers. Built embed Linux application to audit driving exams.}%
    {Python, Django, PostgreSQL, Redis, ffmpeg, Video encoding}

\work{Software Developer / Sep 2014 - Jun 2018}%
    {Bludata - Blumenau, Santa Catarina, Brazil}%
    {Configured and simulated runs of different detector-particle beam interactions. Added a more robust track reconstruction algorithm (General Broken Lines) to the Proteus framework}
    {PHP, Laravel, Sybase, Delphi, C\#, UVC}%

\section{\faList}{SKILLS}

\textbf{Languages:} Python, Go, JavaScript, Ruby, Bash

\noindent\textbf{Tools:} Pandas, Numpy, Pyspark, AWS stack (EMR, Glue, QuickSight, ECS, EC2, S3, etc), Docker, Kubernetes

\noindent\textbf{Other:} Advanced problem-solver, Analytical and data-driven person, Clear communicator and excellent collaborator, Self-directed learner.

\columnbreak

\section{\faGraduationCap}{EDUCATION}

\school{Master's Degree Data Science - 2024*} %
{University of Applied Sciences - Germany} %
{TBD}

\school{MBA Software Engineer - 2020} %
{XP Educação - Minas Gerais, BR} %
{Design and development of a video streaming platform}

\school{Bachelor's Degree in Computer Science - 2015} %
{Fundação Universidade Regional de Blumenau - Santa Catarina, BR} %
{Automatic Pet Feeder Prototype using Raspberry Pi}

\section{\faStar}{AWARDS}

\begin{itemize}[noitemsep]
    \item Ownership Award - As recognition for demonstrating ownership and deliver ahead of expectation to our customers in AWS.
    \item Eplus - Approval of project for incubation. Eplus aimed to be a national knowledge base to help teachers and students and democratize access to good study materials.
\end{itemize}

\section{\faPaintBrush}{OTHER PROJECTS}
\begin{itemize}[noitemsep]
    \item \textbf{Faker}, an open source library to generate fake data in Go with zero dependencies.
    \item My \textbf{personal blog} where I share my latest projects and learns.
\end{itemize}

\section{\faSoccerBallO}{ACTIVITIES / INTERESTS}

Proactive about learning diverse things and happy to discuss those. Favorite activities are playing video games and travel to discover new countries.


\end{multicols}
\end{document}
